\documentclass[a4paper, 11pt]{article}
\title{Jerry Trader Documentation}
\author{JerryHong}
\date{March 2026}
\date{Started December 2025 \\ Last updated: \today}

\usepackage{fontspec}
\usepackage{xeCJK} % for support Chinese.
% Set a CJK monospaced font if available (silences xeCJK unknown-tt warning).
\setCJKmainfont{Microsoft YaHei}
\setCJKmonofont{Microsoft YaHei}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{ragged2e}
\usepackage{array}
\usepackage{seqsplit}
\usepackage{fvextra}
\usepackage{enumitem}
\newcolumntype{Y}{>{\RaggedRight\arraybackslash}X}
% (removed global \texttt redefinition - use \seqsplit manually where needed)

\begin{document}
\maketitle

\pagebreak

\tableofcontents

\pagebreak

\section{Introduction}
Jerry Trader is a multi-language (Python + Rust + React) trading platform designed for real-time US pre-market momentum trading.
This documentation provides an overview of the app's features, architecture, and usage instructions \begin{em}based on my trading strategies\end{em}.

The project follows a monorepo layout:
\begin{itemize}
\item \texttt{python/src/jerry\_trader/} --- Python backend (orchestration, I/O, services)
\item \texttt{rust/src/} --- Rust computation core (compiled via maturin/PyO3 as \texttt{jerry\_trader.\_rust})
\item \texttt{frontend/} --- React + TypeScript frontend (Vite)
\end{itemize}

\pagebreak

\section{Frontend Modules}

\begin{table}[!htbp]
\centering
\footnotesize
\renewcommand{\arraystretch}{1.05}
    \begin{tabularx}{\textwidth}{|>{\RaggedRight\arraybackslash}p{2.5cm}|>{\RaggedRight\arraybackslash}p{2.5cm}|Y|Y|}
\hline
\textbf{Module Type} & \textbf{Sub-View Name} & \textbf{Description} & \textbf{Backend} \\
\hline
rank-list &  & rank list with key metrics & \seqsplit{core.snapshot, static-data-worker, news-worker, core.signals} \\
\hline
stock-detail & fundamentals & stock basic info & \seqsplit{staticdata-worker} \\
\hline
stock-detail & news &  & \seqsplit{news-worker} \\
\hline
overview-chart & overview &  & \seqsplit{overviewchart-management} \\
\hline
overview-chart & focus & focus on one tiker with state segmentation & \seqsplit{overviewchart-management} \\
\hline
chart &  &  & \seqsplit{chart-data-service} \\
\hline
portfolio &  & portfolio and positions & OrderManagement \\
\hline
order-management & placement &  & OrderManagement \\
\hline
order-management & orders &  & OrderManagement \\
\hline
\end{tabularx}
\caption{Module descriptions and their corresponding backends.}
\label{tab:module_descriptions}
\end{table}

\section{Backend Architecture}

\subsection{Package Layout}
The Python backend is organized into the following top-level packages:

    \begin{table}[!htbp]
\centering
\footnotesize
\renewcommand{\arraystretch}{1.15}
    \begin{tabularx}{\textwidth}{|>{\RaggedRight\arraybackslash}p{2.8cm}|Y|>{\RaggedRight\arraybackslash}p{2.5cm}|}
\hline
\textbf{Package} & \textbf{Purpose} & \textbf{Language} \\
\hline
\texttt{core/} & Computation core \& Rust migration boundary & Python + Rust \\
\hline
\texttt{core/snapshot/} & Snapshot processing: ranks, derived metrics, volume tracking & Python $\to$ Rust \\
\hline
\texttt{core/factors/} & Factor engine: trade\_rate, accel, z-scores & Python $\to$ Rust \\
\hline
\texttt{core/signals/} & State/signal detection (QUIET $\leftrightarrow$ ACTIVE) & Python \\
\hline
\texttt{core/news/} & News classification (LLM-based) & Python \\
\hline
\texttt{core/\_bridge.py} & Rust $\leftrightarrow$ Python dispatch (try \_rust, fallback to Python) & Python \\
\hline
BFF & BFF: FastAPI + WebSocket server & Python \\
\hline
\texttt{DataManager/} & Data-serving workers \& servers (static data, news, tick, chart) & Python \\
\hline
\texttt{DataSupply/} & External data sources (Polygon, ThetaData, local files) & Python \\
\hline
\texttt{OrderManagement/} & IBKR order placement, portfolio, persistence & Python \\
\hline
\texttt{MachineLearning/} & ML experimentation (LightGBM) & Python \\
\hline
\texttt{utils/} & Cross-cutting: config, logger, Redis keys, session & Python \\
\hline
\end{tabularx}
\caption{Python backend package layout.}
\label{tab:package_layout}
\end{table}

\pagebreak

\subsection{Computation Core (\texttt{core/})}
The \texttt{core/} package is the \textbf{Rust migration boundary}. Each subpackage follows a compute/orchestration split:

\begin{itemize}
    \item \texttt{compute.py} --- Pure functions \& stateful trackers (\textbf{Rust migration target}). These have planned counterparts in \texttt{rust/src/}.
    \item \texttt{processor.py} / \texttt{engine.py} --- I/O orchestration (Redis, InfluxDB, threads). Stays in Python.
\end{itemize}

The \texttt{\_bridge.py} module provides a try/except dispatch:
\begin{Verbatim}[breaklines=true]
try:
    from jerry_trader._rust import VolumeTracker, compute_ranks
except ImportError:
    from jerry_trader.core.snapshot.compute import VolumeTracker, compute_ranks
\end{Verbatim}

\noindent This allows incremental migration --- Rust implementation when compiled, Python fallback otherwise.

\subsection{Services}

{\small\RaggedRight
\begin{itemize}[leftmargin=*,labelsep=6pt]
    \item \textbf{BackendForFrontend (BFF)} \\
    FastAPI + WebSocket server running on the main machine. Collects and pre-processes (\texttt{\seqsplit{core.snapshot}}); receives and emits rank data and overview-chart data to the frontend.

    \item \textbf{core.snapshot (SnapshotProcessor)} \\
    Receives raw market snapshots from Redis stream, computes ranks and derived metrics (via Rust when available), manages the top-movers subscription set, writes to output Redis stream and InfluxDB.

    \item \textbf{core.factors (FactorManager)} \\
    {\scriptsize\RaggedRight Real-time factor engine. Ingests tick-level trade data.
    Computes trade rate. Computes acceleration. Produces rolling z-scores.
    Outputs to InfluxDB. Uses Redis (HSET) for metadata. Includes historical bootstrap via Polygon API.\par}\justifying

    \item \textbf{core.signals (StateEngine)} \\
    Polls factor HSETs and fires state transition events (QUIET $\to$ ACTIVE, ACTIVE $\to$ QUIET) based on z-score thresholds.

    \item \textbf{core.news (NewsProcessor)} \\
    LLM-based news classification. Determines if news articles are positive catalysts using DeepSeek API.

    \item \textbf{OrderManagement} \\
    Order management system based on Interactive Brokers API. Handles order placement, status callbacks, portfolio and position tracking. Backed by PostgreSQL via SQLAlchemy + Alembic.

    \item \textbf{DataSupply} \\
    External data sources:
    \begin{itemize}
        \item \texttt{snapshotDataSupply} --- market snapshot collection \& replay
        \item \texttt{tickDataSupply} --- real-time tick data (Polygon.io, ThetaData, local Rust replay)
        \item \texttt{staticdataSupply} --- fundamentals, borrow fee, news fetch
        \item \texttt{bootstrapdataSupply} --- historical data loaders
    \end{itemize}

    \item \textbf{DataManager} \\
    Data-serving workers that bridge DataSupply to the BFF:
    \begin{itemize}
        \item \texttt{\seqsplit{static\_data\_worker}} --- fetches fundamentals for subscribed tickers
        \item \texttt{\seqsplit{news\_worker}} --- fetches and caches news
        \item \texttt{\seqsplit{tickdata\_server}} --- serves tick data to frontend and factor engine
        \item \texttt{\seqsplit{chart\_data\_service}} --- historical bar data for TradingView chart
    \end{itemize}

    \item \textbf{utils} \\
    Cross-cutting utilities: config, logger, Redis key naming, session management, path resolution.
\end{itemize}
\par}

\subsection{Rust Migration Roadmap}
\label{sec:rust-roadmap}
The migration from Python \texttt{compute.py} modules to Rust follows a three-step progression, ordered from simplest to most complex:

\begin{enumerate}
    \item \textbf{Step 1: Pure math functions} (\texttt{core/factors/compute.py}) \\
    \texttt{z\_score} and \texttt{price\_accel} --- stateless, no external dependencies.
    This step establishes the full end-to-end workflow: write Rust in \texttt{\seqsplit{lib.rs}},
    run \texttt{maturin develop}, \texttt{\seqsplit{\_bridge.py}} auto-switches,
    existing tests validate correctness, \texttt{RUST\_FACTORS} flips to \texttt{True}.

    \item \textbf{Step 2: Stateful tracker} (\texttt{core/snapshot/compute.py}) \\
    \texttt{VolumeTracker} as a \texttt{\#[pyclass]} with methods ---
    learn stateful Rust objects exposed to Python via PyO3.

    \item \textbf{Step 3: DataFrame operations} (\texttt{core/snapshot/compute.py}) \\
    \texttt{\seqsplit{compute\_ranks}}, \texttt{\seqsplit{compute\_derived\_metrics}}, \texttt{\seqsplit{compute\_weighted\_mid\_price}}
    --- Polars DataFrame in/out, requires the \texttt{pyo3-polars} crate. Most complex.
\end{enumerate}

\noindent\textbf{Note:} \texttt{core/signals/} (StateEngine) is excluded from the Rust migration roadmap.
The signal/state detection logic depends on strategy rules that are not fully decided yet;
it will remain Python-only for the foreseeable future.

\section{Strategy}
This app is designed to implement my personal trading strategies, which focus on US pre-market momentum trading.

\begin{itemize}
\item Trade when tickers are getting active, it has a amount of gains suddenly, we do the momentum trading.

\item And the market has all the attention on this one. cross-section computation.

\item And it has hot news with it.

\item the float shares are relatively low, below 20M is preferred.

\item the country location is not HK or China, etc.
\item price is preferred \$1--\$20
\end{itemize}
\end{document}
